The value of intermediation

### 2022-09-14 src/presentation/presentation.qmd
Add notes to the related literature

@@

::: {.column width="50%"}
Imagine a game with three players:

@@

>>>>

::: {.notes}
 - Further evidence that the Shapley-value is a good bargaining outcome
 - Cooperative bargaining solutions in IO models are finite-player
 - The asymptotics of the weighted value are unknown
 - The literature on hybrid platforms is very recent
 - Shapley-value in a platform setting is new
:::

@@

::: {.column .fragment width="50%"}
Imagine a game with three players:

@@

::: {.column .fragment width="40%"}
And the following achievable profits:
